Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
typo, apostrophe and table

\section{Related Work}
% heather - trips vs locations -> (define) semantic memory vs episodic memory - check references, relate to some work done by SenseCam perhaps?
% cut down GPS usage
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner. Similarly in his seminal paper, \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through ``associative trails'', giving mankind the ability of ``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''. Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one’s sensory experiences about past visits.

@@

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{Participant responses about the memorability, believability, and desirability or Rewinds and photos. The aggregate responses for the two mediums are compared.}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 0.97 & \multicolumn{2}{c|}{0.50} & 0.54 & 0.78 & 0.80 & 0.11 & 0.15 \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\label{table:Rewindvsphotos}
\end{table*}

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.10} & \cellcolor[HTML]{ACDDAA}0.72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.36} \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.48 & 0.56 & 0.53 & 0.54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.90} & 0.60 & 0.25 & 0.56 & 0.59 & 0.50 & 0.60 & 0.52 & 0.56 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.68 & 0.81 & 0.77 & 0.80 & \cellcolor[HTML]{ACDDAA}0.82 & \cellcolor[HTML]{ACDDAA}0.45 & 0.80 & 0.60 & 0.69 & 0.90 & 0.75 & 0.00 & 0.71 & 0.89 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}0.69 & \cellcolor[HTML]{ACDDAA}0.84 & \cellcolor[HTML]{ACDDAA}0.86 & \cellcolor[HTML]{ACDDAA}0.65 & 0.84 & 0.72 & 1.00 & 0.75 & 0.75 & 0.85 & 0.80 & 0.33 & 0.70 & 0.81 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 0.13 & 0.92 & 0.13 & 0.07 & 0.12 & 0.18 & 0.20 & 0.38 & 0.06 & 0.07 & 0.13 & 0.10 & 0.15 & 0.10 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.09} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 0.02} & 0.13 & 0.26 & 0.00 & 0.00 & 0.11 & 0.10 & 0.20 & 0.40 & 0.11 & 0.18 \\ \cline{3-17} 

>>>>

\section{Related Work}
% heather - trips vs locations -> (define) semantic memory vs episodic memory - check references, relate to some work done by SenseCam perhaps?
% cut down GPS usage
\subsection{Digital Memories}
Rewind is guided by literature about mediated memories, which provides a theoretical underpinning behind how the Rewind experience is constructed. \textit{Mediated Memories in the Digital Age} offers inspiration informing the relationship between experiences and memories \cite{van2007mediated}. van Dijck notes, ``Remembering is vital to our well being, because without autobiographical memories we would have no sense of past or future, and we would lack any sense of continuity'' (pg. 3). Rewind aims to give the user this sense of continuity in a time segment which has a past and future. By picking a start and end location from a particular trip and generating a Rewind between these points, the user relives their memories in a continuous manner. Similarly in his seminal paper, \textit{As we may think}, Vannevar Bush described \textit{memex}, the envisioned machinery to store infinite information and to allow free, collective access through ``associative trails'', giving mankind the ability of ``...forgetting the manifold things he does not need to have immediately at hand, with some assurance that he can find them again if they prove important''. Rewind in its most ambitious form, perhaps strives to become a potential counterpart of \textit{memex} for retrieving, and sharing of autobiographical memories of one's sensory experiences about past visits.

@@

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{Participant responses about the memorability, believability, and desirability of Rewinds and photos. The aggregate responses for the two mediums are compared.}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}Rewinds\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}Photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}Rewinds\\ trip\end{tabular} & Photo & Rewinds & Photo & Rewinds \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 97 & \multicolumn{2}{c|}{0.50} & 54 & 78 & 80 & 11 & 15 \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 33} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 0.58} & 0.51 & 0.47 & 1.00 & 1.00 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 1.00} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 75} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 72} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 44} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 52} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 10} & \cellcolor[HTML]{ACDDAA}72 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 36} \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 48 & 56 & 53 & 54 & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 62} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{000000} 90} & 60 & 25 & 56 & 59 & 50 & 60 & 52 & 56 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 68 & 81 & 77 & 80 & \cellcolor[HTML]{ACDDAA}82 & \cellcolor[HTML]{ACDDAA}45 & 80 & 60 & 69 & 90 & 75 & 0 & 71 & 89 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}69 & \cellcolor[HTML]{ACDDAA}84 & \cellcolor[HTML]{ACDDAA}86 & \cellcolor[HTML]{ACDDAA}65 & 84 & 72 & 100 & 75 & 75 & 85 & 80 & 33 & 70 & 81 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & 13 & 92 & 13 & 7 & 12 & 18 & 20 & 38 & 6 & 7 & 13 & 10 & 15 & 10 \\ \cline{3-17} 

@@

\multicolumn{1}{|c|}{} & \multicolumn{1}{c|}{} & \% & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 26} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 9} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 21} & \cellcolor[HTML]{ACDDAA}{\color[HTML]{333333} 2} & 13 & 26 & 0 & 0 & 11 & 10 & 20 & 40 & 11 & 18 \\ \cline{3-17} 
